# Data Science Skills Decal Project 1

**Team Members:**   

**Resumes and Descriptions**

This repo includes the resumes of the following people:

###### EXAMPLE: Leslie Knope (DELETE ME BEFORE SUBMITTING)
* I am currently the Deputy Director of the Parks and Recreation Department of Pawnee, Indiana. In this position, I successfully turned a dangerous pit into a beautiful community park called the Pawnee Commons. I absolutely love my job! I believe that the three most important things in life are friends, waffles, and work... or I mean, waffles, friends, and work. I am just an example of what you need to do, so please delete me before turning your project in.
* Jobs interested in: City Councilwoman, Midwest Regional Director of the National Parks Service, Governor of Indiana

###### [Name of Person that Resume 2 is about]
* 5 sentence summary describing the person from Resume 1.
* Jobs interested in: [List 3 jobs titles that this person is looking for. Be relevant and creative!]

###### [Name of Person that Resume 2 is about]
* 5 sentence summary describing the person from Resume 2.
* Jobs interested in: [List 3 job titles that this person is looking for. Be relevant and creative!]

###### [Name of Person that Resume 3 is about]
* 5 sentence summary describing the person from Resume 3.
* Jobs interested in: [List 3 job titles that this person is looking for. Be relevant and creative!]

###### [(If you have a 4th team member, otherwise delete this entire section) Name of Person that Resume 4 is about]
* 5 sentence summary describing the person from Resume 4.
* Jobs interested in: [List 3 job titles that this person is looking for. Be relevant and creative!]
